---
title: "UKCOTS New Analysis on SATS36"
author: "Ozan Evkaya"
date: "2023-06-16"
output:
  pdf_document: default
  html_document: default
---
```{r, message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(reshape2)
library(boot)
library(ez)
library(lavaan)
library(semPlot)
library(psych)
library(car)
```


# Step 1:Load and clean the dataset
```{r, message=FALSE}
library(readxl)
Pre_2022 <- read_xlsx("SATS_2022_Pre_Anon.xlsx")
Post_2022 <- read_xlsx("SATS_2022_Post_Anon.xlsx")
Pre_2023 <- read_xlsx("SATS_2023_Pre_Anon.xlsx")
Post_2023 <- read_xlsx("SATS_2023_Post_Anon.xlsx")
Demo_2022 <- read_xlsx("SATS_2022_Demographic_Anon.xlsx")

# Simplify the name of each column
# 2022 Pre
Pre_2022 <- rename(Pre_2022, Consent =
                     "(Consent) Do you consent to participating in the study?")
Pre_2022 <- rename(Pre_2022, Validate =
                     "(Validate) Show that you are reading the statements by selecting Strongly Disagree.")
# Get current column names
Pre_2022_colnames_old <- colnames(Pre_2022)
# Generate new names for columns 5 to 33
Pre_2022_new_names <- paste0("Q", 1:29)  # This creates a vector c("Q1", "Q2", ..., "Q29")
# Replace the names of columns 5 to 33 in the 'colnames_old' vector
Pre_2022_colnames_old[5:33] <- Pre_2022_new_names
# Generate new names for columns 35 to the end
Pre_2022_num_remaining_cols <- ncol(Pre_2022) - 34
Pre_2022_new_names <- paste0("Q", 30:36)
# Replace the names of columns 25 to the end in the 'colnames_old' vector
Pre_2022_colnames_old[(34+1):ncol(Pre_2022)] <- Pre_2022_new_names
# Assign the updated names to the dataframe
colnames(Pre_2022) <- Pre_2022_colnames_old
# Remove AnonID HKY and LMT
Pre_2022 <- Pre_2022[!(Pre_2022$AnonID %in% c("HKY", "LMT")), ]

# 2022 Post
Post_2022 <- rename(Post_2022, Consent = "(Consent) Do you consent to participating in the study?")
Post_2022 <- rename(Post_2022, Validate = "(Validate) Show that you are reading the statements by selecting Strongly Agree.")
# Get current column names
Post_2022_colnames_old <- colnames(Post_2022)
# Generate new names for columns 5 to 27
Post_2022_new_names <- paste0("Q", 1:23)  # This creates a vector c("Q1", "Q2", ..., "Q29")
# Replace the names of columns 5 to 27 in the 'colnames_old' vector
Post_2022_colnames_old[5:27] <- Post_2022_new_names
# Generate new names for columns 29 to the end
Post_2022_num_remaining_cols <- ncol(Post_2022) - 28
Post_2022_new_names <- paste0("Q", 24:36)
# Replace the names of columns 25 to the end in the 'colnames_old' vector
Post_2022_colnames_old[(28+1):ncol(Post_2022)] <- Post_2022_new_names
# Assign the updated names to the dataframe
colnames(Post_2022) <- Post_2022_colnames_old
# Remove AnonID HKY and LMT
Post_2022 <- Post_2022[!(Post_2022$AnonID %in% c("HKY", "LMT")), ]

# 2023 Pre
Pre_2023 <- rename(Pre_2023, Consent = "(Consent) Do you consent to participating in the study?")
Pre_2023 <- rename(Pre_2023, Validate = "(Validate) Show that you are reading the statements by selecting Strongly Disagree.")
# Get current column names
Pre_2023_colnames_old <- colnames(Pre_2023)
# Generate new names for columns 5 to 33
Pre_2023_new_names <- paste0("Q", 1:29)  # This creates a vector c("Q1", "Q2", ..., "Q29")
# Replace the names of columns 5 to 33 in the 'colnames_old' vector
Pre_2023_colnames_old[5:33] <- Pre_2023_new_names
# Generate new names for columns 35 to the end
Pre_2023_num_remaining_cols <- ncol(Pre_2023) - 34
Pre_2023_new_names <- paste0("Q", 30:36)
# Replace the names of columns 25 to the end in the 'colnames_old' vector
Pre_2023_colnames_old[(34+1):ncol(Pre_2023)] <- Pre_2023_new_names
# Assign the updated names to the dataframe
colnames(Pre_2023) <- Pre_2023_colnames_old

# 2023 Post
Post_2023 <- rename(Post_2023, Consent = "(Consent) Do you consent to participating in the study?")
Post_2023 <- rename(Post_2023, Validate = "(Validate) Show that you are reading the statements by selecting Strongly Agree.")
# Get current column names
Post_2023_colnames_old <- colnames(Post_2023)
# Generate new names for columns 5 to 27
Post_2023_new_names <- paste0("Q", 1:23)  # This creates a vector c("Q1", "Q2", ..., "Q29")
# Replace the names of columns 5 to 27 in the 'colnames_old' vector
Post_2023_colnames_old[5:27] <- Post_2023_new_names
# Generate new names for columns 29 to the end
Post_2023_num_remaining_cols <- ncol(Post_2023) - 28
Post_2023_new_names <- paste0("Q", 24:36)
# Replace the names of columns 25 to the end in the 'colnames_old' vector
Post_2023_colnames_old[(28+1):ncol(Post_2023)] <- Post_2023_new_names
# Assign the updated names to the dataframe
colnames(Post_2023) <- Post_2023_colnames_old

```


```{r}
glimpse(Pre_2022)
```



Then we count the number of available and unavailable results

```{r, message=FALSE}
# Pre 2022
# Count the number of "No, I do not consent" in the Consent column
Pre_2022_consent_count <- Pre_2022 %>%
  filter(Consent == "No, I do not consent") %>%
  nrow()

print(paste0("Number of 'No, I do not consent' responses: ", 
             Pre_2022_consent_count))

# Remove the rows with "No, I do not consent" in the Consent column
Pre_2022_clean_consent <- Pre_2022 %>%
  filter(Consent != "No, I do not consent")

# Count the number of responses that are not "Strongly Disagree" in the Validate column
Pre_2022_validate_count <- Pre_2022_clean_consent %>%
  filter(Validate != "Strongly Disagree") %>%
  nrow()

print(paste0("Number of responses not 'Strongly Disagree' in the Validate column: ",
             Pre_2022_validate_count))

# Remove the rows without "Strongly Disagree" in the Validate column
Pre_2022_clean <- Pre_2022_clean_consent %>%
  filter(Validate == "Strongly Disagree")

# Calculate the number of original rows (total responses)
Pre_2022_total_responses <- nrow(Pre_2022)

# Calculate the number of remaining rows (available results)
Pre_2022_available_results <- nrow(Pre_2022_clean)

# Calculate the number of unavailable results
Pre_2022_unavailable_results <- Pre_2022_total_responses - 
  Pre_2022_available_results

# Print the results
print(paste("Total responses in Pre_2022: ", Pre_2022_total_responses))
print(paste("Available results in Pre_2022: ", Pre_2022_available_results))
print(paste("Unavailable results in Pre_2022: ", Pre_2022_unavailable_results))

```

The number of unavailable results is not equal to the sum of Number of 'No, I do not consent' responses and Number of responses not 'Strongly Disagree' in the Validate column because some results show "Yes, I consent" but NA in every column.


```{r, message=FALSE}
# Post 2022
# Count the number of "No, I do not consent" in the Consent column
Post_2022_consent_count <- Post_2022 %>%
  filter(Consent == "No, I do not consent") %>%
  nrow()

print(paste0("Number of 'No, I do not consent' responses: ", Post_2022_consent_count))

# Remove the rows with "No, I do not consent" in the Consent column
Post_2022_clean_consent <- Post_2022 %>%
  filter(Consent != "No, I do not consent")

# Count the number of responses that are not "Strongly Disagree" in the Validate column
Post_2022_validate_count <- Post_2022_clean_consent %>%
  filter(Validate != "Strongly Agree") %>%
  nrow()

print(paste0("Number of responses not 'Strongly Agree' in the Validate column: ",
             Post_2022_validate_count))

# Remove the rows without "Strongly Disagree" in the Validate column
Post_2022_clean <- Post_2022_clean_consent %>%
  filter(Validate == "Strongly Agree")

# Calculate the number of original rows (total responses)
Post_2022_total_responses <- nrow(Post_2022)

# Calculate the number of remaining rows (available results)
Post_2022_available_results <- nrow(Post_2022_clean)

# Calculate the number of unavailable results
Post_2022_unavailable_results <- Post_2022_total_responses - 
  Post_2022_available_results

# Print the results
print(paste("Total responses in Post_2022: ", Post_2022_total_responses))
print(paste("Available results in Post_2022: ", Post_2022_available_results))
print(paste("Unavailable results in Post_2022: ", Post_2022_unavailable_results))

```

```{r, message=FALSE}
# # Pre 2023
# # Count the number of "No, I do not consent" in the Consent column
# Pre_2023_consent_count <- Pre_2023 %>%
#   filter(Consent == "No, I do not consent") %>%
#   nrow()
# 
# print(paste0("Number of 'No, I do not consent' responses: ", Pre_2023_consent_count))
# 
# # Remove the rows with "No, I do not consent" in the Consent column
# Pre_2023_clean_consent <- Pre_2023 %>%
#   filter(Consent != "No, I do not consent")
# 
# # Count the number of responses that are not "Strongly Disagree" in the Validate column
# Pre_2023_validate_count <- Pre_2023_clean_consent %>%
#   filter(Validate != "Strongly Disagree") %>%
#   nrow()
# 
# print(paste0("Number of responses not 'Strongly Disagree' in the Validate column: ",
#              Pre_2023_validate_count))
# 
# # Remove the rows without "Strongly Disagree" in the Validate column
# Pre_2023_clean <- Pre_2023_clean_consent %>%
#   filter(Validate == "Strongly Disagree")
# 
# # Calculate the number of original rows (total responses)
# Pre_2023_total_responses <- nrow(Pre_2023)
# 
# # Calculate the number of remaining rows (available results)
# Pre_2023_available_results <- nrow(Pre_2023_clean)
# 
# # Calculate the number of unavailable results
# Pre_2023_unavailable_results <- Pre_2023_total_responses - 
#   Pre_2023_available_results
# 
# # Print the results
# print(paste("Total responses in Pre_2023: ", Pre_2023_total_responses))
# print(paste("Available results in Pre_2023: ", Pre_2023_available_results))
# print(paste("Unavailable results in Pre_2023: ", Pre_2023_unavailable_results))
```

```{r, message=FALSE}
# # Post 2023
# # Count the number of "No, I do not consent" in the Consent column
# Post_2023_consent_count <- Post_2023 %>%
#   filter(Consent == "No, I do not consent") %>%
#   nrow()
# 
# print(paste0("Number of 'No, I do not consent' responses: ", Post_2023_consent_count))
# 
# # Remove the rows with "No, I do not consent" in the Consent column
# Post_2023_clean_consent <- Post_2023 %>%
#   filter(Consent != "No, I do not consent")
# 
# # Count the number of responses that are not "Strongly Disagree" in the Validate column
# Post_2023_validate_count <- Post_2023_clean_consent %>%
#   filter(Validate != "Strongly Agree") %>%
#   nrow()
# 
# print(paste0("Number of responses not 'Strongly Agree' in the Validate column: ",
#              Post_2023_validate_count))
# 
# # Remove the rows without "Strongly Disagree" in the Validate column
# Post_2023_clean <- Post_2023_clean_consent %>%
#   filter(Validate == "Strongly Agree")
# 
# # Calculate the number of original rows (total responses)
# Post_2023_total_responses <- nrow(Post_2023)
# 
# # Calculate the number of remaining rows (available results)
# Post_2023_available_results <- nrow(Post_2023_clean)
# 
# # Calculate the number of unavailable results
# Post_2023_unavailable_results <- Post_2023_total_responses - Post_2023_available_results
# 
# # Print the results
# print(paste("Total responses in Post_2023: ", Post_2023_total_responses))
# print(paste("Available results in Post_2023: ", Post_2023_available_results))
# print(paste("Unavailable results in Post_2023: ", Post_2023_unavailable_results))

```

```{r, message=FALSE}
# Create a new dataframe to hold the summary
summary_available <- data.frame(
  Table = c("Pre 2022", "Post 2022", "Pre 2023", "Post 2023"),
  Available_Results = c(Pre_2022_available_results, Post_2022_available_results, 
                        Pre_2023_available_results, Post_2023_available_results),
  Unavailable_Results = c(Pre_2022_unavailable_results, Post_2022_unavailable_results, 
                          Pre_2023_unavailable_results, Post_2023_unavailable_results),
  Total_responses = c(Pre_2022_total_responses, Post_2022_total_responses, 
                      Pre_2023_total_responses, Post_2023_total_responses)
)

print(summary_available)
```

# Step 2: Convert answers to numbers of each question

```{r, warning=FALSE, message=FALSE}
library(dplyr)
# Define a vector for the responses
responses <- c("Strongly Agree", "Agree", "Somewhat Agree", "Neither Agree or Disagree", "Somewhat Disagree", "Disagree", "Strongly Disagree")

# Define a vector for the scores
scores <- c(7, 6, 5, 4, 3, 2, 1)

# Define the column names
columns <- c(paste0("Q", 1:8), paste0("Q", 10:36))  # Exclude Q9

# Define negatively worded questions
negatively_worded_questions <- c("Q4", "Q5", "Q7", "Q8", "Q11", "Q13", "Q15", "Q16", "Q18","Q21", "Q24", "Q25", "Q26", "Q28", "Q30", "Q33", "Q34", "Q35", "Q36") # replace these with your actual negatively worded questions


recode_responses <- function(column) {
  dplyr::recode(column,
                "Strongly Agree" = 7,
                "Agree" = 6,
                "Somewhat Agree" = 5,
                "Neither Agree or Disagree" = 4,
                "Somewhat Disagree" = 3,
                "Disagree" = 2,
                "Strongly Disagree" = 1,
                .default = NA_real_)
}

# Convert responses to scores
#for (column in columns) {
#  Pre_2022_clean[[column]] <- recode(Pre_2022_clean[[column]], !!!setNames(scores, responses))
  
#  # Reverse scores for negatively worded questions
#  if (column %in% negatively_worded_questions) {
#    Pre_2022_clean[[column]] <- 8 - as.numeric(Pre_2022_clean[[column]])
#  }
#}

#Pre_2022_clean <- Pre_2022_clean %>%
#  mutate(across(all_of(columns), ~ recode_responses(.x))) %>%
#  mutate(across(all_of(negatively_worded_questions), ~ 8 - .x))

# Convert responses to scores and add as new columns
Pre_2022_clean <- Pre_2022_clean %>%
  mutate(across(all_of(columns), ~ recode_responses(.x), .names = "num_{col}")) %>%
  mutate(across(all_of(negatively_worded_questions), ~ 8 - get(paste0("num_", cur_column())), .names = "rev_{col}"))

#####################################################
# Combine the original and recoded columns as needed
# Here, we keep the original columns and add new columns with scores and reversed scores
Pre_2022_clean_new <- Pre_2022_clean %>%
  select(RowID, AnonID, Date, Consent, starts_with("num_"), starts_with("rev_"))

##################### POST ##############################
#######################################################
columns_post <- paste0("Q", 1:36)

#for (column in columns) {
#  Post_2022_clean[[column]] <- recode(Post_2022_clean[[column]], 
#                                      !!!setNames(scores, responses))
  
#  # Reverse scores for negatively worded questions
#  if (column %in% negatively_worded_questions) {
#    Post_2022_clean[[column]] <- 8 - Post_2022_clean[[column]]
#  }
#}

Post_2022_clean <- Post_2022_clean %>%
  mutate(across(all_of(columns_post), ~ recode_responses(.x), .names = "num_{col}")) %>%
  mutate(across(all_of(negatively_worded_questions), ~ 8 - get(paste0("num_", cur_column())), .names = "rev_{col}"))


Post_2022_clean_new <- Post_2022_clean %>%
  select(RowID, AnonID, Date, Consent, starts_with("num_"), starts_with("rev_"))

#for (column in columns) {
#  Pre_2023_clean[[column]] <- recode(Pre_2023_clean[[column]], 
#                                     !!!setNames(scores, responses))
  
  # Reverse scores for negatively worded questions
#  if (column %in% negatively_worded_questions) {
#    Pre_2023_clean[[column]] <- 8 - Pre_2023_clean[[column]]
#  }
#}

#for (column in columns) {
#  Post_2023_clean[[column]] <- recode(Post_2023_clean[[column]],
#                                      !!!setNames(scores, responses))
  
#  # Reverse scores for negatively worded questions
#  if (column %in% negatively_worded_questions) {
#    Post_2023_clean[[column]] <- 8 - Post_2023_clean[[column]]
#  }
# }

```

# Step 3: Calculate Scores of each component

```{r, message=FALSE}
# Pre 2022
# Create new columns for the means
Pre_2022_clean_new$Affect <- rowMeans(Pre_2022_clean_new[c("num_Q3", "num_Q4", "num_Q15", 
                                                           "num_Q18", "num_Q19", "num_Q28")], na.rm = TRUE)

Pre_2022_clean_new$Cognitive_Competence <- rowMeans(Pre_2022_clean_new[c("num_Q5", "num_Q11", "num_Q26", 
                                                            "num_Q31", "num_Q32", "num_Q35")], na.rm = TRUE)

#!!!!!!!!!!!!!ignore Q9
Pre_2022_clean_new$Value <- rowMeans(Pre_2022_clean_new[c("num_Q7", "num_Q10", "num_Q13", "num_Q16", "num_Q17", 
                                                          "num_Q21", "num_Q25", "num_Q33")], na.rm = TRUE)

Pre_2022_clean_new$Difficulty <- rowMeans(Pre_2022_clean_new[c("num_Q6", "num_Q8", "num_Q22", 
                                                 "num_Q24", "num_Q30", "num_Q34", "num_Q36")], na.rm = TRUE)

Pre_2022_clean_new$Interest <- rowMeans(Pre_2022_clean_new[c("num_Q12", "num_Q20", 
                                                             "num_Q23", "num_Q29")], na.rm = TRUE)

Pre_2022_clean_new$Effort <- rowMeans(Pre_2022_clean_new[c("num_Q1", "num_Q2", 
                                                           "num_Q14", "num_Q27")], na.rm = TRUE)

```

```{r, message=FALSE}
# Post 2022
# Create new columns for the means
Post_2022_clean_new$Affect <- rowMeans(Post_2022_clean_new[c("num_Q3", "num_Q4", "num_Q15", 
                                                     "num_Q18", "num_Q19", "num_Q28")], na.rm = TRUE)

Post_2022_clean_new$Cognitive_Competence <- rowMeans(Post_2022_clean_new[c("num_Q5", "num_Q11", 
                                                    "num_Q26", "num_Q31", "num_Q32", "num_Q35")], na.rm = TRUE)
#!!!!!!!!!!!!!ignore Q9
Post_2022_clean_new$Value <- rowMeans(Post_2022_clean_new[c("num_Q7", "num_Q10", "num_Q13", "num_Q16",
                                                    "num_Q17", "num_Q21", "num_Q25", "num_Q33")], na.rm = TRUE)

Post_2022_clean_new$Difficulty <- rowMeans(Post_2022_clean_new[c("num_Q6", "num_Q8", "num_Q22", 
                                            "num_Q24", "num_Q30", "num_Q34", "num_Q36")], na.rm = TRUE)

Post_2022_clean_new$Interest <- rowMeans(Post_2022_clean_new[c("num_Q12", "num_Q20", 
                                                               "num_Q23", "num_Q29")], na.rm = TRUE)

Post_2022_clean_new$Effort <- rowMeans(Post_2022_clean_new[c("num_Q1", "num_Q2", "num_Q14", "num_Q27")], na.rm = TRUE)

```

```{r, message=FALSE}
# Pre 2023
# Create new columns for the means
#Pre_2023_clean$Affect <- rowMeans(Pre_2023_clean[c("Q3", "Q4", "Q15", "Q18", "Q19",
#                                                   "Q28")], na.rm = TRUE)
#Pre_2023_clean$Cognitive_Competence <- rowMeans(Pre_2023_clean[c("Q5", "Q11", "Q26",
#                                                                 "Q31", "Q32", 
#                                                                 "Q35")], 
#                                                na.rm = TRUE)
#Pre_2023_clean$Value <- rowMeans(Pre_2023_clean[c("Q7", "Q9", "Q10", "Q13", "Q16",
#                                                  "Q17", "Q21", "Q25", "Q33")],
#                                 na.rm = TRUE)
#Pre_2023_clean$Difficulty <- rowMeans(Pre_2023_clean[c("Q6", "Q8", "Q22", "Q24",
#                                                       "Q30", "Q34", "Q36")], 
#                                      na.rm = TRUE)
#Pre_2023_clean$Interest <- rowMeans(Pre_2023_clean[c("Q12", "Q20", "Q23", "Q29")], 
#                                    na.rm = TRUE)
#Pre_2023_clean$Effort <- rowMeans(Pre_2023_clean[c("Q1", "Q2", "Q14", "Q27")], 
#                                  na.rm = TRUE)

```

```{r, message=FALSE}
# Post 2023
# Create new columns for the means
#Post_2023_clean$Affect <- rowMeans(Post_2023_clean[c("Q3", "Q4", "Q15", "Q18", 
#                                                     "Q19", "Q28")], na.rm = TRUE)
#Post_2023_clean$Cognitive_Competence <- rowMeans(Post_2023_clean[c("Q5", "Q11",
#                                                                   "Q26", "Q31",
#                                                                   "Q32", "Q35")], 
#                                                 na.rm = TRUE)
#Post_2023_clean$Value <- rowMeans(Post_2023_clean[c("Q7", "Q9", "Q10", "Q13", 
#                                                    "Q16", "Q17", "Q21", "Q25",
#                                                    "Q33")], na.rm = TRUE)
#Post_2023_clean$Difficulty <- rowMeans(Post_2023_clean[c("Q6", "Q8", "Q22", "Q24",
#                                                         "Q30", "Q34", "Q36")], 
#                                       na.rm = TRUE)
#Post_2023_clean$Interest <- rowMeans(Post_2023_clean[c("Q12", "Q20", "Q23", "Q29")],
#                                     na.rm = TRUE)
#Post_2023_clean$Effort <- rowMeans(Post_2023_clean[c("Q1", "Q2", "Q14", "Q27")],
#                                   na.rm = TRUE)

```



# Step 4: Calculate statistical characteristics and observe the distributions of each component


```{r, message=FALSE}
# Pre 2022
# Calculate statistical characteristics
Pre_2022_summary <- summary(Pre_2022_clean_new[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")])
print(Pre_2022_summary)

# Calculate variance
for(column in c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")) {
  cat("Variance of", column, ":", var(Pre_2022_clean_new[[column]], na.rm = TRUE), "\n")
}

# Melt the data into long format for easier plotting
Pre_2022_long <- melt(Pre_2022_clean_new[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")], 
                      id.vars = NULL, variable.name = "Component", value.name = "Score")

# Create a histogram
ggplot(Pre_2022_long, aes(x = Score)) +
  geom_histogram(binwidth = 0.5, fill = "blue", alpha = 0.5) +
  facet_wrap(~Component, scales = "free", nrow = 3, ncol = 2) +
  theme_minimal() +
  xlab("Score") +
  ylab("Count") +
  ggtitle("Distribution of Component Scores of Pre 2022")

```

```{r, message=FALSE}
# Post 2022
# Calculate statistical characteristics
Post_2022_summary <- summary(Post_2022_clean_new[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")])
print(Post_2022_summary)

# Calculate variance
for(column in c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")) {
  cat("Variance of", column, ":", var(Post_2022_clean_new[[column]], na.rm = TRUE), "\n")
}

# Melt the data into long format for easier plotting
Post_2022_long <- melt(Post_2022_clean_new[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")], id.vars = NULL, variable.name = "Component", 
                      value.name = "Score")

# Create a histogram
ggplot(Post_2022_long, aes(x = Score)) +
  geom_histogram(binwidth = 0.5, fill = "blue", alpha = 0.5) +
  facet_wrap(~Component, scales = "free", nrow = 3, ncol = 2)  +
  theme_minimal() +
  xlab("Score") +
  ylab("Count") +
  ggtitle("Distribution of Component Scores of Post 2022")
```

Then we compare the distribution of scores for each component between the two results, now we just look at the overall picture of each result instead of matching the pre-course and post-course results for the same person:

```{r, message=FALSE}
# boxplots of 2022 
# Add a new column to each dataframe to indicate whether it's pre or post
Pre_2022_clean_new$Course <- "Pre"
Post_2022_clean_new$Course <- "Post"

Pre_2022_clean_new %>% select(RowID, AnonID, Date, Consent, Affect, Cognitive_Competence, Value, 
                              Difficulty, Interest, Effort, Course)


# Combine the two dataframes
combined_2022 <- rbind(Pre_2022_clean_new, Post_2022_clean_new)

# Reshape the data into long format for easier plotting
df_long_2022 <- melt(combined_2022[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort", "Course")], id.vars = "Course", 
                     variable.name = "Component", value.name = "Score")

# Convert 'Course' to a factor and specify the level order
df_long_2022$Course <- factor(df_long_2022$Course, levels = c("Pre", "Post"))

# Create boxplots
ggplot(df_long_2022, aes(x = Component, y = Score, fill = Course)) +
  geom_boxplot() +
  theme_minimal() +
  xlab("Component") +
  ylab("Score") +
  ggtitle("Comparison of Component Scores Between Pre- and Post-Course in 2022")


# bar charts
# Calculate mean scores
df_mean_2022 <- df_long_2022 %>% 
  group_by(Course, Component) %>%
  summarise(Mean_Score = mean(Score, na.rm = TRUE))
# Create side-by-side bar chart
ggplot(df_mean_2022, aes(x = Component, y = Mean_Score, fill = Course)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.6) +
  theme_minimal() +
  xlab("Component") +
  ylab("Mean Score") +
  ggtitle("Comparison of Mean Component Scores Between Pre-Course and Post-Course")

# Calculate variance for each component in both dataframes
variance_pre <- sapply(Pre_2022_clean[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")], var, na.rm = TRUE)
variance_post <- sapply(Post_2022_clean[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")], var, na.rm = TRUE)

# Prepare a dataframe for plotting
df_variance_2022 <- data.frame(
  Component = rep(names(variance_pre), 2),
  Variance = c(variance_pre, variance_post),
  Course = rep(c("Pre", "Post"), each = length(variance_pre))
)

# Create side-by-side bar charts
ggplot(df_variance_2022, aes(x = Component, y = Variance, fill = Course)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.6) +
  theme_minimal() +
  xlab("Component") +
  ylab("Variance") +
  ggtitle("Comparison of Variance of Component Scores Between Pre-Course and Post-Course")


```



```{r, message=FALSE}
# Pre 2023
# Calculate statistical characteristics
#Pre_2023_summary <- summary(Pre_2023_clean[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")])
#print(Pre_2023_summary)

# Calculate variance
#for(column in c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")) {
#  cat("Variance of", column, ":", var(Pre_2023_clean[[column]], na.rm = TRUE), "\n")
#}

# Melt the data into long format for easier plotting
#Pre_2023_long <- melt(Pre_2023_clean[, c("Affect", "Cognitive_Competence", "Value",
#                                         "Difficulty", "Interest", "Effort")], 
#                      id.vars = NULL, variable.name = "Component", 
#                      value.name = "Score")

# Create a histogram
#ggplot(Pre_2023_long, aes(x = Score)) +
#  geom_histogram(binwidth = 0.5, fill = "blue", alpha = 0.5) +
#  facet_wrap(~Component, scales = "free") +
#  theme_minimal() +
#  xlab("Score") +
#  ylab("Count") +
#  ggtitle("Distribution of Component Scores of Pre 2023")

```

```{r, message=FALSE}
# Post 2023
# Calculate statistical characteristics
#Post_2023_summary <- summary(Post_2023_clean[, c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")])
#print(Post_2023_summary)

# Calculate variance
#for(column in c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")) {
#  cat("Variance of", column, ":", var(Post_2023_clean[[column]], na.rm = TRUE), "\n")
#}

# Melt the data into long format for easier plotting
#Post_2023_long <- melt(Post_2023_clean[, c("Affect", "Cognitive_Competence", 
#                                           "Value", "Difficulty", "Interest",
#                                           "Effort")], id.vars = NULL,
#                       variable.name = "Component", 
#                      value.name = "Score")

# Create a histogram
#ggplot(Post_2023_long, aes(x = Score)) +
#  geom_histogram(binwidth = 0.5, fill = "blue", alpha = 0.5) +
#  facet_wrap(~Component, scales = "free") +
#  theme_minimal() +
#  xlab("Score") +
#  ylab("Count") +
#  ggtitle("Distribution of Component Scores of Post 2023")
```

# Step 5: Combine the pre and post results for the same person

```{r, message=FALSE}
# Merge the two dataframes on 'AnonID'
# Add a new column to each dataframe to indicate whether it's pre or post
Pre_2022_clean_new$Course <- "Pre"
Post_2022_clean_new$Course <- "Post"

combined_2022_individual <- merge(Pre_2022_clean_new, Post_2022_clean_new, by = "AnonID", 
                                  suffixes = c("_pre", "_post"))

# Check the first few rows of the combined dataframe
head(combined_2022_individual)

components_2022 <- c("Affect", "Cognitive_Competence", "Value", "Difficulty", 
                     "Interest", "Effort")

# Plot scatterplots for each component
#for (component in components_2022) {
#    p <- ggplot(combined_2022_individual, aes_string(x = paste0(component, "_pre"), 
#                                                     y = paste0(component, "_post"))) +
#        geom_point() +
#        geom_abline(slope = 1, intercept = 0, color = "red") +
#        labs(title = paste("Comparison of", component, "Scores"),
#             x = paste("Pre-course", component),
#             y = paste("Post-course", component))
#    
#    print(p)
#}

```

Some new boxplots and graphs for the filtered data

```{r}
# Reshape the data into long format for easier plotting
df_long_2022 <- melt(combined_2022_individual[, c("Affect_pre", "Cognitive_Competence_pre", "Value_pre", "Difficulty_pre", "Interest_pre", "Effort_pre",
                                                  "Affect_post", "Cognitive_Competence_post", "Value_post", "Difficulty_post", "Interest_post", "Effort_post", "Course_pre", "Course_post")], 
                     id.vars = c("Course_pre", "Course_post"), 
                     variable.name = "Component", value.name = "Score")

# Adjust the 'Course' column to indicate pre or post course
df_long_2022 <- df_long_2022 %>%
  mutate(Course = case_when(
    grepl("_pre", Component) ~ "Pre",
    grepl("_post", Component) ~ "Post"
  ),
  Component = gsub("_pre|_post", "", Component))

# Convert 'Course' to a factor and specify the level order
df_long_2022$Course <- factor(df_long_2022$Course, levels = c("Pre", "Post"))

# Create boxplots
ggplot(df_long_2022, aes(x = Component, y = Score, fill = Course)) +
  geom_boxplot() +
  theme_minimal() +
  xlab("Component") +
  ylab("Score") +
  ggtitle("Comparison of Component Scores Between Pre- and Post-Course in 2022") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("Boxplots_pre_post.png")

```

Summary statistics on the remaining 132 participants only!

```{r}
# Define the components and corresponding columns
components <- c("Affect", "Cognitive_Competence", "Value", "Difficulty", "Interest", "Effort")
pre_cols <- paste0(components, "_pre")
post_cols <- paste0(components, "_post")

# Calculate the statistics for pre- and post-course data
stats_pre <- combined_2022_individual %>%
  summarise(across(all_of(pre_cols), list(mean = ~mean(., na.rm = TRUE), 
                                          median = ~median(., na.rm = TRUE), 
                                          variance = ~var(., na.rm = TRUE))))

round(stats_pre, 3)

stats_post <- combined_2022_individual %>%
  summarise(across(all_of(post_cols), list(mean = ~mean(., na.rm = TRUE), 
                                           median = ~median(., na.rm = TRUE), 
                                           variance = ~var(., na.rm = TRUE))))

round(stats_post, 3)

```



```{r, message=FALSE}
# Calculate difference in scores for each component

for (component in components_2022) {
  combined_2022_individual[paste(component, "diff", sep = "_")] <- combined_2022_individual[paste(component, "post", sep = "_")] - combined_2022_individual[paste(component, "pre", sep = "_")]
}

# Check the first few rows of the updated dataframe
head(combined_2022_individual)

```

```{r, warning=FALSE, message=FALSE}
# Calculate statistical characteristics for each difference column
summary_diff_2022 <- summary(combined_2022_individual[, paste0(components_2022, "_diff")])
print(summary_diff_2022)

# Calculate variance for each difference column
for(column in paste0(components_2022, "_diff")) {
  cat("Variance of", column, ":", var(combined_2022_individual[[column]], na.rm = TRUE), "\n")
}

# Create boxplots to show the difference scores
diff_2022 <- melt(combined_2022_individual[, paste0(components_2022, "_diff")], variable.name = "Component_Diff", value.name = "Score_Diff")

ggplot(diff_2022, aes(x = Component_Diff, y = Score_Diff)) +
  geom_boxplot(fill = "blue", alpha = 0.5) +
  theme_minimal() +
  xlab("Component Difference") +
  ylab("Score Difference") +
  geom_hline(yintercept = c(-0.5, 0.5), linetype = "dashed", color = "red")+
  ggtitle("Boxplots of Score Differences for Each Component")

df_long_2022 <- melt(combined_2022_individual, id.vars = "AnonID", 
                     measure.vars = c("Affect_diff", "Cognitive_Competence_diff",
                                      "Value_diff", "Difficulty_diff", 
                                      "Interest_diff", "Effort_diff"),
                     variable.name = "Component", value.name = "Score_Difference")

# Create scatterplot
ggplot(df_long_2022, aes(x = AnonID, y = Score_Difference)) +
  geom_point() +
  facet_wrap(~ Component, scales = "free") +
  theme_minimal() +
  xlab("Individual") +
  ylab("Score Difference (Post - Pre)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Difference in Component Scores for Each Individual")
```


# Step 7: Cronbach's alpha

Cronbach's Alpha is a measure of internal consistency, that is, how closely related a set of items are as a group. A "high" value of alpha (close to 1) is often used as evidence that the items measure an underlying (latent) construct.


```{r, warning=FALSE}
library(psych)
# Pre 2022
components_pre <- list(
  Affect_pre = c("num_Q3_pre", "num_Q4_pre", "num_Q15_pre", "num_Q18_pre", "num_Q19_pre", "num_Q28_pre"),
  Cognitive_Competence_pre = c("num_Q5_pre", "num_Q11_pre", "num_Q26_pre", "num_Q31_pre", "num_Q32_pre", "num_Q35_pre"),
  Value_pre = c("num_Q7_pre", "num_Q9_pre", "num_Q10_pre", "num_Q13_pre", "num_Q16_pre", "num_Q17_pre", "num_Q21_pre", 
            "num_Q25_pre", "num_Q33_pre"),
  Difficulty_pre = c("num_Q6_pre", "num_Q22_pre", "num_Q8_pre", "num_Q24_pre", "num_Q30_pre", "num_Q34_pre", "num_Q36_pre"), 
  Interest_pre = c("num_Q12_pre", "num_Q20_pre", "num_Q23_pre", "num_Q29_pre"),
  Effort_pre = c("num_Q1_pre", "num_Q2_pre", "num_Q14_pre", "num_Q27_pre")
)

for(name in names(components_pre)) {
  alpha_score <- alpha(combined_2022_individual[components_pre[[name]]])
  print(paste(name, "Cronbach's Alpha:", alpha_score$total$raw_alpha))
}
```


